\documentclass{article} % For LaTeX2e
\usepackage{nips14submit_e,times}
\usepackage{hyperref}
\usepackage{url}
\usepackage{graphicx}
\usepackage{subcaption}
%\documentstyle[nips14submit_09,times,art10]{article} % For LaTeX 2.09


\title{An Analysis of the Web Graph Utilizing Apache Flink}
\author{
Hung Chang \\
\and
Philip Raschke
}

% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to \LaTeX{} to determine where to break
% the lines. Using \AND forces a linebreak at that point. So, if \LaTeX{}
% puts 3 of 4 authors names on the first line, and the last on the second
% line, try using \AND instead of \And before the third author name.

\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}

%\nipsfinalcopy % Uncomment for camera-ready version

\begin{document}

\maketitle

\begin{abstract}
This project aims to achieve a comprehensive analysis of the structure of the World-Wide-Web. Therefore, we used the data sets provided by the Web Data Commons project which extracted the web graph from the Common Crawl project. A small example data set was used while implementing algorithms that compute degree, connectivity, PageRank, closeness and betweenness of the nodes of the graph. Graph analyzing tools were used to evaluate the algorithms' validity. The computations then were run on a four node cluster on larger data sets to retrieve results of the whole web graph.
\end{abstract}

\section{Problem Statement}
\input{problem}

\section{Methodology}
\input{methodology}

\section{Experiments}
\input{experiments}

\section{Conclusion}
\input{conclusion}

\subsubsection*{References}

\small{
	[1] Kang, U., Papadimitriou, S., Sun, J., Watson, T., \& Tong, H. (2011). Centralities in large networks: Algorithms and observations. 
	[2] WDC - Download the 2012 Hyperlink Graph. URL: http://webdatacommons.org/hyperlinkgraph/2012-08/download.html Last accessed: 10th of February 2015
	[3] Chakkaradhari, J., Schelter S., Markl, V. (2014). Large Scale Centrality Measures in Apache Flink and Apache Giraph.
	[4] Meusel, R., Vigna, S., Bizer, C. \& Lehmberg, O. (2014). Graph Structure in the Web — Revisited
}

\end{document}
